TacticToe: Learning to Prove with Tactics

### 2018-02-19 tactictoe_jv.tex
Concl

To improve the quality of the predicted tactics,
we would like to predict other type of arguments independently, as it was done
for theorems. In this direction, the most interesting arguments to
predict next are terms as they are ubiquitous in tactics. Further along the way,
new tactics could be created by programming them with any construction
available in \sml. There is also something to be gain by
having a better guidance for the search.
That is why se also want to experiment with stronger machine learning algorithm
such as deep neural networks as a model for the policy and evaluation in MCTS.
This quality of this model could be enhanced by additional data augmentation by
training and testing existing and synthesized tactics.
Conjecturing suitable intermediate steps could also allow \tactictoe to solve
a problem which requires a long proof by decomposing it into multiple easy
steps.

>>>>

To improve the quality of the predicted tactics,
we would like to predict other type of arguments independently, as it was done
for theorems. In this direction, the most interesting arguments to
predict next are terms as they are ubiquitous in tactics. Further along the way,
new tactics could be created by programming them with any construction
available in \sml.
The proof search guidance can also be improved, for example by considering
stronger machine learning algorithms
such as deep neural networks as a model for the policy and evaluation in MCTS.
The quality of such models could be enhanced by
training and testing existing and synthesized tactics.
Conjecturing suitable intermediate steps could also allow \tactictoe to solve
problems which require long proofs by decomposing it into multiple easier
steps.
